Impact of asymmetric tail-dependence in extreme climatic events on extinction risk in population ecology

### 2019-04-18 MainText.Rmd
Results for Q2 written

<!--Q2 : metapopulation results : density dependence with extreme tail dep. copula-->
We found density-dependence metapopulation models with $n=5$ patches in noisy 
environment showed similar patterns for extinction risk as density-independent 
metapopulation model showed in earlier studies [BIVAN paper]. For each density-dependent 
model listed in Table \ref{tab_model_summary}, we observed higher (or lower) extinction risk for 
the metapopulations when noises across multiple patches were left- (or right) tail dependent.
But that observation remained valid when the model parameter, usually growth rate $(r)$, of each model was 
sufficiently low so that under-compensatory dynamics (monotonous approach towards
its stable equilibrium) for the deterministic analog of the model was ensured. When the model 
was in over-compensatory regime (oscillatory approach towards stable equilibrium) for higher 
value of $r$, we observed right (or left) tail dependent noise caused higher (or lower) extinction 
risk for the metapopulations. All models were consistent with our prediction (see Q2 from \nameref{intro}) 
across local and global dispersal (Figs. \ref{fig_extrisk_allmodel_localdisp} and 
\ref{SM-fig_extrisk_allmodel_globaldisp}).

<!--For local dispersal : all model summary : Fig. 2, individual model : Fig. S3-S8-->

<!--For global dispersal : all model summary : Fig. S2, individual model : Fig. S9-S14-->

<!--Q3 : metapopulation results : switching near rc for d=0, Fig. 3-->

>>>>

<!--Q2 : metapopulation results : density dependence with extreme tail dep. copula-->
<!--For local dispersal : all model summary : Fig. 2, individual model : Fig. S3-S8-->
<!--For global dispersal : all model summary : Fig. S2, individual model : Fig. S9-S14-->

We found density-dependence metapopulation models (with $n=5$ patches) in noisy 
environment showed similar patterns for extinction risk as density-independent 
metapopulation model showed in earlier studies [BIVAN paper]. For each density-dependent 
model listed in Table \ref{tab_model_summary}, we observed higher (or lower) extinction risk for 
the metapopulations when noises across multiple patches were left- (or right) tail dependent.
But that observation remained valid when the model parameter, usually growth rate $(r)$, of each model was 
sufficiently low so that under-compensatory dynamics (monotonous approach towards
its stable equilibrium) for the deterministic analog of the model was ensured. When the model 
was in over-compensatory regime (oscillatory approach towards stable equilibrium) for higher 
value of $r$, we observed right (or left) tail dependent noise caused higher (or lower) extinction 
risk for the metapopulations. Figs. \ref{fig_extrisk_allmodel_localdisp} shows variation of extinction risk 
against local dispersal rate ($d$) for six density dependent metapopulation models 
where growth rate $r$ was taken either from under-compensatory or from over-compensatory 
regime. We also got similarly consisent results with 
our prediction (see Q2 from \nameref{intro}) for global 
dispersal (Fig. \ref{SM-fig_extrisk_allmodel_globaldisp}). 
Figs. (\ref{SM-fig_ricker_risk_local_disp_scl_1} - \ref{SM-fig_risk_local_disp_abrewer_r_vary_scl_0.6}) 
shows how extinction risk changed against local dispersal rate for a whole range
of $r$, whereas Figs. (\ref{SM-fig_ricker_risk_global_disp_scl_1} - 
\ref{SM-fig_risk_global_disp_abrewer_r_vary_scl_0.6}) 
represents the same but when global dispersal took place between patches. 
Both case showed the signature of 
"rescue-effect" (i.e. by lowering extinction risk) when there was 
a finite dispersal compared to the one with 
$d=0$.

<!--Q3 : metapopulation results : switching near rc for d=0, Fig. 3-->
To examine (Q3), we evaluated extinction risk for each metapopulation model for a wide
